Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-01-25 tacl.tex
Edits to end

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{xspace}
\usepackage[pdftex]{graphicx}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) when proper names which we consider outside the scope of FS identification (as discussed earlier) are excluded. 
% TJB: is this a subset of proper names? the "excepting ..." qualification is a bit vague
Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams. The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
 In a POS-tagged corpus, potential gaps can be identified by a POS regular expression. This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus.  Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $i+1$-grams which are also over the threshold. 
% TJB: this last sentence is a bit opaque

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_0,..., w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}

\noindent
where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively. 
% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation

@@

Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
% TJB: greedy how (in terms of ordering of nodes)? frequency based as per above?

In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
\begin{itemize}
\item We limit the total number of relevant nodes to 5. When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation.
% TJB: say more -- relative change how?
\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
\item Many nodes have a minLPR which is a little larger than 1. There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
\end{itemize}

@@

We evaluate our approach across three different languages including evaluation sets derived from four different corpora. In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}. To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus. Lemmatization included removing all inflectional marking from both words and POS tags. For English, we took the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.

The other two languages we include in our evaluation are Croatian and Japanese. Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages. For Croatian, we used the X corpus, a collection of X. The POS regex for Croatian included XXX. .... For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus. We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}, and performed noun chunking based on a simple regex over the POS output.
% TJB: worth including the respective POS regexes in an appendix?

\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model. We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: based on written guidelines derived from the definitions of Wray \cite{Wray08} and at least one practice round,three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.

@@

The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}. As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose. The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages. Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian. The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.

In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method. Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.

@@

Though the results across the four corpora are reasonably similar with respect to overall f-score, there are a significant discrepancies. By using the UNIDIC morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages. The result is that there are many more FS for Japanese. Precision is very high, and recall is relatively low. Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to f-score, which explains why the full model is not the best in that one case.  Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types. One idea for future work is to automatically adapt to the particular properties of the input language/corpus in order to ensure a good balance between precision and recall.

At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in a minimum counts of in the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times. This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations. One idea we are actively pursing is modifying the calculation of the LPR metric to integrating uncertainty due to low counts.

There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news. The ICWSM and the Japanese corpus, on the other hand, are mostly blogs. Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres. The fact that last than 20\% of the FS derived from the BNC appears in the lexicon for the ICWSM is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.

We were interested in addressing Croatian and Japanese in part because of their tendency towards relatively free word order, and whether allowing gaps in our FS would help with these languages. We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less. Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints. The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS. This phenomena actually highlights a problem with the current model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently. Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.

A third, more ambitious option would be to switch to a dependency representation. This option actually requires very little change to the structure of the model presented here, since all the basic relationships in the lattice as well as the minLPR measure could be straightforwardly defined in terms of subgraphs instead of strings. One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using of FS to improve parsing. A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \ie \ex{no amount of * can}.

As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations. One of the major benefits of this model as compared to alternatives is the relative ease at which additional kinds of interactions between nodes could be implemented. Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, for instance, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not. Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure. Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaiticity.

Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning. Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, we found that the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary for to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal. We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.

Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that f-scores become unreliable when there are very few positive examples. To do a independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling. Rather than brute force annotation, one option we could consider is a adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.

@@

We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice. Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages. A tool which implements the method as well as the acquired lexicons and test sets are available here.\footnote{removed for anonymity}

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{xspace}
\usepackage{paralist}
\usepackage[pdftex]{graphicx}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names. 
Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams. The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
 In a POS-tagged corpus, potential gaps can be identified by a POS regular expression. This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus.  Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $(i+1)$-grams which are also over the threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_0,..., w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively.

@@

Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.

In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
\begin{compactitem}
\item We limit the total number of relevant nodes to 5. When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation.
\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
\item Many nodes have a minLPR which is a little larger than 1. There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
\end{compactitem}

@@

We evaluate our approach across three different languages including evaluation sets derived from four different corpora. In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}. To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM corpus, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus. Lemmatization included removing all inflectional marking from both words and POS tags. For English, we took the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.

The other two languages we include in our evaluation are Croatian and Japanese. Both these languages are relatively free-word order, providing valuable test cases of the challenges associated with using an $n$-gram approach to FS extraction in such languages. For Croatian, we used the X corpus, a collection of X. The POS regex for Croatian included XXX. .... For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus. We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}, and performed noun chunking based on a simple regex over the POS output.
% TJB: worth including the respective POS regexes in an appendix?

\newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model. Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model. We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above. Based on written guidelines derived from the definitions of \newcite{Wray08} and at least one practice round, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.

@@

The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}. As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose. The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages. Generally, clearing and overlap node interactions offer a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian. The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.

In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method. Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.

@@

Though the results across the four corpora are reasonably similar with respect to overall F-score, there are significant discrepancies. By using the UNIDIC morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages. The result is that there are many more FS for Japanese. Precision is very high, and recall is relatively low. Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to F-score, which explains why the full model is not the best in that one case.  Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM corpus, or almost 14\% of all $n$-gram types. One idea for future work is to automatically adapt to the particular properties of the input language/corpus in order to ensure a good balance between precision and recall.

At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times. This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations. One idea we are actively pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.

There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news. The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages. Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres. The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.

We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether allowing gaps in our FS would help with these languages. We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less. Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints. The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS. This phenomena actually highlights a problem with the current model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently. Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
% TJB: would be good to have some examples of gapped expressions to better make this point (yes, space permitting)

A third, more ambitious option would be to switch to a dependency representation. This option actually requires very little change to the structure of the model presented here, since all the basic relationships in the lattice as well as the minLPR measure could be straightforwardly defined in terms of subgraphs instead of strings. One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using FS to improve parsing. A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \eg \ex{no amount of \gap can}.

As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations. One of the major benefits of this model as compared to alternatives is the relative ease with which additional kinds of interactions between nodes could be implemented. Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not. Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure. Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaticity.

Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning. Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, but the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal. We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at a majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.

Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that F-scores become unreliable when there are very few positive examples. To do an independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling. Rather than brute force annotation, one option we could consider is adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.

@@

We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice. Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages. A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{removed for anonymity}
